---
format:
  gfm:
    default-image-extension: ""
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rome

<!-- badges: start -->
[![R-CMD-check](https://github.com/Huber-group-EMBL/rome/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Huber-group-EMBL/rome/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

rome is a minimal R package to read and write multiscale OME-Zarr files.

It also provides helper and methods to manipulate the resulting `ome_zarr` objects the same way one would manipulate traditional arrays in R. For example, you can subset an `ome_zarr` object using the `[` operator, and the subsetting will be applied to all levels of the multiscale OME-Zarr object.

## Installation

You can install the development version of rome like so:

``` r
# install.packages("pak")
pak::pak("Huber-group-EMBL/rome")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
#| label: example
library(rome)
s3_client <- paws.storage::s3(
  config = list(
    credentials = list(anonymous = TRUE),
    region = "auto",
    endpoint = "https://uk1s3.embassy.ebi.ac.uk"
  )
)
x <- ome_read(
  "https://uk1s3.embassy.ebi.ac.uk/idr/zarr/v0.4/idr0076A/10501752.zarr", s3_client = s3_client, lazy = TRUE
)
plot(x, all = TRUE)
```
